Incentivizing Exploration with Unbiased History

### 2018-11-02 llevel-overview.tex
rm shit

In the $L$-level policy, such boundary case occurs for each
intermediate level $l\in \{2, \ldots, l-1\}$, but issue mentioned
above does not get naturally resolved as in some of these boundary
cases---the ratios between the upper and lower bounds of $\Delta$ rise
from $\Theta(\sqrt{\log(T)})$ to $\Theta(\log(T))$, and it would
require more observations from level $(l-2)$ to distinguish two arms
at level $l$. The reason for this larger disparity is that, except the
first level, we can no longer guarantee sufficient number of pulls of
each arm. For example, in as shown in Figure
\ref{fig:llevel-connecting}, when we talk about having enough arm $a$
pulls in the history observed by agents in $G_{l,1,1}$, it could be
that only agents in group $G_{l-1,1,1}$ are pulling arm $a$ and it
also could be that most agents in groups
$G_{l-1,1,1},G_{l-1,1,2},...,G_{l-1,1,\NG}$ are pulling arm
$a$. Therefore our estimate of the number of arm $a$ pulls can be off
by an $\NG=\Theta(\log(T))$ multiplicative factor. This finally makes
the boundary cases harder to deal with.

>>>>

In the $L$-level policy, such boundary case occurs for each
intermediate level $l\in \{2, \ldots, l-1\}$, but issue mentioned
above does not get naturally resolved as in some of these boundary
cases---the ratios between the upper and lower bounds of $\Delta$ rise
from $\Theta(\sqrt{\log(T)})$ to $\Theta(\log(T))$, and it would
require more observations from level $(l-2)$ to distinguish two arms
at level $l$. The reason for this larger disparity is that, except the
first level, we can no longer guarantee sufficient number of pulls of
each arm. For example, as shown in Figure \ref{fig:llevel-connecting},
when we talk about having enough arm $a$ pulls in the history observed
by agents in $G_{l,1,1}$, it could be that only agents in group
$G_{l-1,1,1}$ are pulling arm $a$ and it also could be that most
agents in groups $G_{l-1,1,1},G_{l-1,1,2},...,G_{l-1,1,\NG}$ are
pulling arm $a$. Therefore our estimate of the number of arm $a$ pulls
can be off by an $\NG=\Theta(\log(T))$ multiplicative factor. This
finally makes the boundary cases harder to deal with.
